\documentclass[11pt, a4paper, leqno]{article}
\usepackage{a4wide}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{float, afterpage, rotating, graphicx}
\usepackage{epstopdf}
\usepackage{longtable, booktabs, tabularx}
\usepackage{fancyvrb, moreverb, relsize}
\usepackage{eurosym, calc}
% \usepackage{chngcntr}
\usepackage{amsmath, amssymb, amsfonts, amsthm, bm}
\usepackage{caption}
\usepackage{mdwlist}
\usepackage{xfrac}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{url} 
\usepackage{subcaption}
\usepackage{minibox}
% \usepackage{pdf14} % Enable for Manuscriptcentral -- can't handle pdf 1.5
% \usepackage{endfloat} % Enable to move tables / figures to the end. Useful for some submissions.


\usepackage[
    natbib=true,
    bibencoding=inputenc,
    bibstyle=authoryear-ibid,
    citestyle=authoryear-comp,
    maxcitenames=3,
    maxbibnames=10,
    useprefix=false,
    sortcites=true,
    backend=biber
]{biblatex}
\AtBeginDocument{\toggletrue{blx@useprefix}}
\AtBeginBibliography{\togglefalse{blx@useprefix}}
\setlength{\bibitemsep}{1.5ex}
\addbibresource{refs.bib}





\usepackage[unicode=true]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    anchorcolor=black,
    citecolor=black,
    filecolor=black,
    menucolor=black,
    runcolor=black,
    urlcolor=black
}


\widowpenalty=10000
\clubpenalty=10000

\setlength{\parskip}{1ex}
\setlength{\parindent}{0ex}
\setstretch{1.5}


\begin{document}

\title{European Factor Stockpicking and Screener\thanks{Jonathan Willnow, University Bonn. Email: \href{mailto:jona.willnow@hotmail.de}{\nolinkurl{jona [dot] willnow [at] hotmail [dot] de}}.}}

\author{Jonathan Willnow}

\date{
    {\bf Preliminary -- please do not quote}
    \\[1ex]
    \today
}

\maketitle


\begin{abstract}
    The focus of this project is to build an interactive tool that helps individual investors in their buying decisions of individual stock. 
    The project tackles several aspects to lead to betetr ibnformed decisions: First, I deliberately omit the names of the stocks and report only the ticker symbol.
    This should help individuals to not bias themselves when tehy see an popular or unpopular stock since the decision should be purely based on the fundamentals.
    Secondly, apart from reporting standart metrics, I calculate the empirically proven Fama French Asset Pricing Factors. Thirdly, I come up with an on Score to score the stocks
    with respect to the asset pricing factors and reported metrics. This Score is not an ultimatively assasement since it does not capture all neccessary informations, 
    but investors can use it to get a first insight into a stock.
    This project is based on sraped stocks for Germany, Europe, North-America and Japan and collects the metrics used for assesment and calculation of the facotrs
    from finance.yahoo.com. The long term plan is to automate this project such that it serves as a reliable, automated way to screen stocks and improve stockpicking decisions.
\end{abstract}
\clearpage

\section{Introduction} % (fold)
\label{sec:introduction}
Stock market participation increased in the last years. While this is overall a positive develoment, many investors lack tools to base their investments on or are solely using their
gut feeling. While there are lots of tools available, I could not find a free tool that allows a comparison of stocks based on the Fama French Asset Pricing Factors - so I 
decided to build it myself. As this is work in progress, it is not available right now for the broad audience, but I shared the results in a developed Dash-App with a big german speaking 
stock picking community, called "Kleine Finanzzeitung". This allows users to access my results and my research without having a proper background in programming and git.
The Dash-App can be found here: \url{https://stockpickingapp.herokuapp.com}



\section{Methodology}
The idea apperas simple: There exist more than only one risk factor $r_f$,  that determines the
performance of a portfolio (here, portfolio is assumed to be a index/ market portfolio).
ama and French came up with the Fama and French three factor model that includes
the size of firms, their book-to-market values, and their excess return on the market. In other words, 
the three factors used are $SMB$ (small minus big), $HML$ (high minus low), and $r_f$, the
market return return less the risk-free rate of return. Building up on their work, many other
factors have been researched and found like the Fama French Quality Factor and Conservative 
Asset factor or the Carhartd Momentum Factor. While the Momentum Factor finds strong 
empirical support like the other factors, this project sofar is limited to the factors 
found by Fama and French. 
A selection of individual Stocks is available for Europe, Germany, Japan and North America
that was collected using several scrapers and validation mehtods. To obtain reliable metrics
the metrics are collected from https://finance.yahoo.com
using the functionality of the python packe urllib.requests. The so obtained metrics were then 
used to compute the introduced factors according to the work of Fama and French. To present the 
results and allow for easy filtering, I decided to deploy this simple Dash App.


\section{Code}
As this project was part of the course Effective Programming Practices for Economists by Prof. von Gaudecker, the corresponding repository 
that is available on github follows \citet{GaudeckerEconProjectTemplates}. The code for this repo can be found on \url{https://github.com/JonathanWillnow/european_factor_stockpicking_screener}

\section{How to run the code}
Please refer to the README.md file for how to run the project and its tasks.

\section{Further Development and Outlook}

% section introduction (end)




\setstretch{1}
\printbibliography
\setstretch{1.5}




% \appendix

% The chngctr package is needed for the following lines.
% \counterwithin{table}{section}
% \counterwithin{figure}{section}

\end{document}
